---
title: "W_UP_01"
author: "Racheal Adeneye"
date: "spring 2025"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(pushups~position,data=mydata)
```

It looks like the skill players are doing a lot more pushups than the line players are doing.

It looks like no line player did as many as 40 pushups. However, 25% of the skill players did about 35 pushups.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```

Q1 of the skill players is higher than Q3 of the line players.
There are 8 line players and 22 skill players.

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```
The probability of getting a result like this is, in high school terms, .000009421. We do not think this happened by accident. We think the right interpretation is that the skill players do more pushups than the line players.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

First we copied the plot command from the helper file and changed the action plot to boxplot and changed the agreements to match our data and wrote comments on the boxplot. Then we gathered the numerical descriptive results (using the command from our helper file) and changed the agreements again and also commented on the data we had. Finally, we ran a t-test using the command from the helper file and once again changed the agreements and changed our scientific notation p-value to a decimal value, as we did in high school.